Active Learning from Blackbox to Timed Connectors

### 2016-04-20 shortpaper/paper.tex
.

\subsection{L* Algorithm}
The whole L* algorithm can be briefly concluded as follows. In this algorithm,
\begin{itemize}
  \item \emph{observation table} is a widely-used data structure to describe the hypothesis.
\end{itemize}
Please refer to \cite{DBLP:conf/sfm/SteffenHM11, DBLP:journals/iandc/Angluin87} for further details.
\begin{algorithm} 
  \caption{L*} 
  \label{alg:lstar}
  \KwIn{Oracle interfaces $mq,eq$, Input actions $\mathcal{I}$}
  \KwOut{Observation table $obs$} 
  $obs.S$ initialized as empty\;
  $obs.D$ initialized as $\{[i]|i\in\mathcal{I}\}$\;
  \Repeat{$ce=true$}{
    $obs$ = EncloseHypothesis($mq$, $\mathcal{I}$, $obs$)\;
    $ce=eq(obs)$\;
    \If {$ce\neq true$} {
      $obs.D$.append(Suffix$(ce, obs)$)\;
    }
  }
  \Return $obs$\; 
\end{algorithm}

The L* algorithm takes a set of input actions $\mathcal{I}$ and a oracle interface (which plays the
role of SUL) as its parameters. And it returns a so-called \emph{observation table} as the final
hypothesis. (Observation table is a widely-used data structure, which can represent a Mealy machine
by its external observation.)
In each iteration, the algorithm will:
\begin{enumerate}
  \item \emph{Enclose the hypothesis.} Active learning is very similar to a breadth-first-search
    process on an unknown Mealy machine. At first, only the initial state is visible to us. We then
    explore different input actions and check if they can lead to some state that is already known.
    If every edge targets to an explored state, we will say that the hypothesis is \emph{closed}.
  \item \emph{Equivalence checking.} After the hypothesis is enclosed, we need to check if the
    current hypothesis is equivalent to the real model. Such $eq$ operation returns a
    \emph{true} if they are equivalent, or a counter-example if not.
  \item \emph{Counter-example Analysis.}  
\end{enumerate}

>>>>

\subsection{L* Algorithm}
The whole L* algorithm can be briefly concluded as follows. In this algorithm,
\begin{itemize}
  \item \emph{Observation table} is a widely-used data structure to describe the hypothesis. In such
    tables, rows correspond to a states (denoted as $S$), and columns correspond to \emph{suffixes}
    (denoted as $D$).
  \item \emph{Suffixes} are used to distinguish different states. For example, two input sequences
    $a$ and $b$ lead to the same state iff. $\forall c\in\mathcal{I}^*, mq(ac) = mq(bc)$.
\end{itemize}
Please refer to \cite{DBLP:conf/sfm/SteffenHM11, DBLP:journals/iandc/Angluin87} for further details.
\begin{algorithm} 
  \caption{L*} 
  \label{alg:lstar}
  \KwIn{Oracle interfaces $mq,eq$, Input actions $\mathcal{I}$}
  \KwOut{Observation table $obs$} 
  $obs.S$ initialized as empty\;
  $obs.D$ initialized as $\{[i]|i\in\mathcal{I}\}$\;
  \Repeat{$ce=true$}{
    $obs$ = EncloseHypothesis($mq$, $\mathcal{I}$, $obs$)\;
    $ce=eq(obs)$\;
    \If {$ce\neq true$} {
      $obs.D$.append(Suffix$(ce, obs)$)\;
    }
  }
  \Return $obs$\; 
\end{algorithm}

The L* algorithm takes a set of input actions $\mathcal{I}$ and a oracle interface (which plays the
role of SUL) as its parameters. And it returns a so-called \emph{observation table} as the final
hypothesis. (Observation table is a widely-used data structure, which can represent a Mealy machine
by its external observation.)
In each iteration, the algorithm will:
\begin{enumerate}
  \item \emph{Enclose the hypothesis.} Active learning is very similar to a breadth-first-search
    process on an unknown Mealy machine. At first, only the initial state is visible to us. We then
    explore different input actions and check if they can lead to some state that is already known.
    If every edge targets to an explored state, we will say that the hypothesis is \emph{closed}.
  \item \emph{Equivalence checking.} After the hypothesis is enclosed, we need to check if the
    current hypothesis is equivalent to the real model. Such $eq$ operation returns a
    \emph{true} if they are equivalent, or a counter-example if not.
  \item \emph{Counter-example Analysis.} As mentioned before, we use suffixes to distinguish
    different states. Consequently, lack of proper suffix may lead to counter-examples. By the
    \emph{suffix} function, we can analyze the counter-example and find out which suffix is left out.
\end{enumerate}
